Turbo fast no compromise gravitational wave parameter estimation

### 2022-12-08 src/tex/ms.tex
Add paragraph related to optimization to-do

% Show injection pp plot
To quantify the accuracy of our pipeline, we show th
\subsection{Real event parameter estimation}

@@

% JIT overhead
Jax's JIT compilation drastically reduce the computational time to evaluate the
likelihood. However, it comes with a compilation overhead when the likelihood is
evaluated for the first time. We observed the compilation time could depends on
the device where the code will be run. This is expected since Jax leverage
Accelerated Linear Algebra (XLA) to take advantage of accelerators, which means
Jax needs to compile the code for the specific device according to its
architecture. On an Nvidia A100 GPU, the compilation overhead could go up to 5
minutes for the waveform we are using. For the cases we have studied, the time
needed to obtain converging results on a A100 is about 2-3 minutes. This means
the compilation overhead is dominating the wall-clock time of the specific PE
run we considered. To utilize our implementation to its full potential, we are
looking into ways to reduce the compilation overhead, or to cache the
compilation results to avoid paying the compilation overhead for every events.

>>>>

% Show injection pp plot
The result of the injection studies is shown in \ref{fig: ppplot}.

\subsection{Real event parameter estimation}

@@

% JIT overhead
Jax's JIT compilation drastically reduce the computational time to evaluate the
likelihood. However, it comes with a compilation overhead when the likelihood is
evaluated for the first time. We observe that the compilation time could depends
on the device where the code will be run. This is expected since Jax leverage
Accelerated Linear Algebra (XLA) to take advantage of accelerators, which means
Jax needs to compile the code for the specific device according to its
architecture. On an Nvidia A100 GPU, the compilation overhead could go up to 5
minutes for the waveform we are using. For the cases we have studied, the time
needed to obtain converging results on a A100 is about 2-3 minutes. This means
the compilation overhead is dominating the wall-clock time of the specific PE
run we considered. To utilize our implementation to its full potential, we are
looking into ways to reduce the compilation overhead, or to cache the
compilation results to avoid paying the compilation overhead for every events.

% Faster maximum likelihood finder

Another overhead we are looking into reducing is the time needed to find the
reference waveform for heterodyning the likelihood. Currently we are using
\texttt{differential evolution} available in \texttt{scipy} to find the waveform
parameters which maximize the likelihood. Since \texttt{differnetial evolution}
has not been implemented in Jax, and the Jax waveform we use is not compatible
with parallelization scheme in the \texttt{scipy} library, it takes around 5
minutes \kw{Benchmark it in the code and make this number precise.} to find the
reference waveform parameters for GW170817. There are two ways to improve the
performance in finding the parameters of the reference waveform. First, we can
explore different optimization strategy that is more compatible with the
strength of our pipeline, in particular differentiability of our likelihood and
the possibility to evaluate many waveforms in parallel with a GPU. Particle
swarm or stochastic gradient descent methods are promising candidate which we
intend to investigate in the future.

Another way to reduce the time of finding maximum likelihood waveform is to
incoporate marginalization of extrinsic parameters to reduce the dimensionality
of the optimization problem. Currently we simutaneously maximize all 11 GW
parameters, which is unnecessarily complicated and expensive. There are
long-existing marginalization schemes over extrinsic parameters such as merger
time and phase, which can find the corresponding maximum likelihood waveform
much more efficiently when compared to differential evolution. We expect
implementing these marginalization schemes will reduce the time needed to find
the reference waveform parameters by obtaining the extrinsic parameters and by
reducing the dimensionality of the optimization problem for the intrinsic
parameters.
